On The Impact of Atoms of Confusion in JavaScript Code

### 2021-10-20 4_Result.tex
comparacao com trabalhos anteriores

\begin{table}[htbp]
\caption{Summary of the correctness analysis}
\label{tab:difference-correctness}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
  Atom & Confusing Code & Clean Code & $\Delta$(\%)  \\ \midrule
  Comma Operator                &  28 &  65 & +132   \\ 
  Automatic Semicolon Insertion &  32 &  68 & +112   \\ 
  Post-Increment                &  48 &  64 & +33    \\ 
  Omitted Curly Braces          &  47 &  58 &  +23   \\
  Assignment as Value           &  56 &  68 &  +21   \\ 
  Implicit Predicate            &  58 &  68 &  +17   \\ 
  Logic as Control Flow         &  41 &  48 &  +17   \\ 
  Ternary Operator              &  60 &  66 &  +10   \\ 
  Pre-Increment                 &  50 &  53 &  +6    \\ 
  Arithmetic as Logic           &  64 &  63 &  -2    \\ \bottomrule

@@

Finally, we also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant \emph{education} or participant \emph{experience} impact correctness. Although the results suggest that experience impacts correctness, the education level does not. As such, we replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistical difference is less significant for those developers with more than ten years of experience.

@@

%% Regarding the first question we 
%% address in the survey (\emph{Do code snippets that contain atoms of confusion produce a higher error rate than snippets where the atom is removed?}), we found evidence that the atoms of confusion lead programmers to misunderstand JavaScript code. We also realized that just one atom whose correction has a non-significant improvement in the percentage of correct answers---we found an improvement of at least 15\% in the correct answers when removing the confusing code for seven atoms (out of ten atoms we consider in the survey).

@@

\begin{table}[htbp]
\caption{Time in seconds to submit a correct answer}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
Atom & Confusing Code & Clean Code & $\Delta$(\%) \\ \midrule
Comma Operator & 87.67 & 20.84 & -76.23 \\ 
Automatic Semicolon Insertion & 46.08 & 22.04 & -52.17 \\ 
Post-Increment & 28.70 & 25.67 & -10.56 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 \\ 
Ternary Operator & 41.80 & 39.34 & -5.90 \\ 
Pre-Increment & 30.71 & 42.45 & 38.19 \\  
Arithmetic as Logic & 28.82 & 37.20 & 29.06 \\ \bottomrule
\end{tabular}
\label{tab:difference-time-taken}
\end{scriptsize}
}
\end{table}

@@

 \centering
 \begin{tabular}{lccc|cc}
   \toprule
Atom  & Chi-square test & Odds Ratio          & CI & Mann-Whitey U test & Cliff's Delta \\ 
     &         & (misunderstanding)  &                    & (workload)             & \\ \midrule
Comma Operator & 1.1727e-10 & 19.02 & (6.60, 68.22) & 5.8249e-08 & -0.53 \\ 
Automatic Semicolon Insertion & 5.8352e-11 & 39.33 & (9.21, 356.62) & 0.09802 & -0.16 \\ 
Post-Increment & 0.0015279 & 4.83 & (1.73, 15.74) & 0.12006 & 0.15 \\ 
Omitted Curly Braces & 0.050962 & 2.35 & (1.00, 5.77) & 0.92529 & -0.01 \\ 
Assignment as Value & 0.0034775 & 8.39 & (1.81, 79.12) & 0.82681 & 0.02 \\ 
Implicit Predicate & 0.01123 & 6.95 & (1.46, 66.56) & 0.0029039 & -0.29 \\ 
Logic as Control Flow & 0.292 & 1.54 & (0.73, 3.28) & 7.5862e-05 & -0.39 \\ 
Ternary Operator & 0.15896 & 2.73 & (0.74, 12.57) & 0.24073 & -0.12 \\ 
Pre-Increment & 0.70147 & 1.25 & (0.55, 2.85) & 0.0062981 & 0.27 \\ 
Arithmetic as Logic & 1 & 0.84 & (0.22, 3.12) & 0.01723 & 0.23 \\ 
    \bottomrule
 \end{tabular}
 \label{tab:hypothesis-testing}
 \end{table*}

@@

\begin{table}[!htb]
    \centering
    \caption{Summary of participants' preferences for code snippets \emph{with} and
      \emph{without} atom candidates. The participants were only presented the code snippets, without any indication about whether one was confusing or not. 
      Participants were also allowed to choose Neutral when they thought both sides were equally readable.}
    \begin{tabular}{lrrr}\toprule
      & \multicolumn{3}{c}{\textsc{Preference (\%)}} \\
      \cmidrule(lr){2-4}
         Atom           & \multicolumn{1}{c}{Confusing}
                                      &  \multicolumn{1}{c}{Clean}
                                               & \multicolumn{1}{c}{Neutral} \\ \midrule
         Comma Operator                  & 0  & 100    & 0     \\
         Automatic Semicolon Insertion  & 0  & 80     & 0     \\
         Post-Increment                  & 20 & 73.33  & 6.67  \\
         Omitted Curly Braces            & 0  & 100    & 0     \\
         Assignment as Value             & 20 & 60     & 20    \\
         Implicit Predicate              & 20 & 73.33  & 6.67  \\
         Logic as Control Flow           & 20 & 60     & 20    \\
         Ternary Operator                & 60 & 26.67  & 13.3  \\
         Pre-Increment                   & 40 & 46.67  & 13.33 \\ 
         Arithmetic as Logic             & 0  & 93.33  & 6.67  \\ \midrule
         \textsc{overall}                & 18 & 71.33  & 8.64  \\
         \bottomrule
    \end{tabular}
    \label{tab:interview-results1}
\end{table}

\subsubsection*{The Participants' perceptions of the atom candidates}
Supporting the results of the survey, Table~\ref{tab:interview-results1}
 shows that for eight out of the
10 scenarios surveyed, the majority of the respondents prefer the version of the
code without the atom candidate.
In no case the \emph{neutral}
ratio was higher than the option for the Clean version.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Ternary Operator atom candidate the participants prefer the Confusing version, instead of the Clean one. We show the code snippets for the Ternary Operator in Figure~\ref{code:ternary}. Even for this atom candidate, some participants who preferred the left-hand side version (confusing) still believed that the right-hand side version (clean) was more readable. The following quotes were extracted from the transcripts with
% three interviewees:
two interviewees:

@@

\noindent\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript, caption=\emph{Left-hand side} (using the \emph{Ternary Operator} atom).]
let config = {size: 3, isActive: false};
const_config = config.isActive === true 
             ? config 
             : {size: 10};
console.log(_config.size);
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript, caption=\emph{Right-hand side} (without the atom).]
let config = {size: 3, isActive: false}
let _config;
if(config.isActive === true) {
  _config = config;
}
else{
   _config = {size: 10};
}
console.log(_config.size);
\end{lstlisting}
\end{minipage}
\caption{Example of a pair of code snippets used in the interview. This case explores the use of the \emph{Ternary Operator atom of confusion}}
\label{code:ternary}
\vspace{-0.2cm}
\end{figure*}

@@

We mined \minedprojects open source JavaScript repositories to understand how
often atoms of confusion arise in real software. 
Similarly to previous studies~\cite{DBLP:conf/msr/GopsteinZFC18,DBLP:journals/ese/MedeirosLAAKRG19}, which investigate
the prevalence of atoms of confusion in open source \clang and \cpplang projects, we found that atoms of confusion
frequently arise in JavaScript open source systems. For instance, the six most frequently found atoms
occur in at least 80\% of the projects. Considering the extremes, atom candidates Ternary Operator and Implicit Predicate were found in all repositories we mined,
while Comma Operator occurred in only 15\% of them (as seen in Table~\ref{tab:occurrences-summary}).

@@

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Tue Apr 13 09:34:35 2021
\begin{table}[ht]
\centering
\caption{Summary of atom candidate occurrences on our dataset.}
\setlength\tabcolsep{2pt} % default value: 6pt
\begin{tabular}{lrc}%c}
  \toprule
Atom & Projects & Occurr./KLOC \\%& Frequency \\ 
  \midrule
Implicit Predicate & 100\% & 19.89 \\%&  intensively used \\ 
  Ternary Operator & 100\% & 10.16 \\%&  intensively used \\ 
  Omitted Curly Braces & 91.67\% & 6.61 \\%&  intensively used \\ 
  Post Increment & 90.28\% & 5.62 \\%&  intensively used \\ 
  Pre Increment & 83.33\% & 1.04 \\%& commonly used \\ 
  Assignment as Value & 81.94\% & 1.02 \\%& commonly used \\ 
  Logic as Control Flow & 56.94\% & 0.95 \\%& commonly used \\ 
  Automatic Semicolon Insertion & 33.33\% & 0.13 \\%& commonly used \\ 
  Arithmetic as Logic & 23.61\% & 0.02 \\%& rarely used \\ 
  Comma Operator & 15.28\% & 0.03 \\%& rarely used \\
   \bottomrule
\end{tabular}
\label{tab:occurrences-summary}
\end{table}

Considering all JavaScript projects in our dataset, we found a total of \num{364873} atom candidates, though four atoms are responsible
for 92.97\% of this total: Implicit Predicate, Post Increment, Ternary Operator, and Omitted Curly Braces. The first two, based on the results of Section~\ref{sec:survey-resuts}, can be considered atoms of confusion. The remaining atom
candidates comprise \num{25621} occurrences combined, 7.03\% of the total number of occurrences.
The Comma Operator and Arithmetic as Logic atoms are the ones that arise less
frequently (0.001\% in total with 232 and 165 occurrences, respectively).

% Regarding frequency, we proceeded with a classification of \emph{atom occurrence}
% based on thresholds used in a previous
% study~\cite{DBLP:journals/ese/MedeirosLAAKRG19}. 
% Atoms that occur 1000 times are classified as \textit{rarely used} while atoms with more than \num{10000} occurrences are classified as \textit{highly used}; \textit{commonly used} atoms occur in between.
We calculated the frequency of each atom per KLOC.
The four atoms mentioned in the previous paragraph,
 Implicit Predicate, Post Increment, Ternary Operator, and Omitted Curly Braces, occur frequently in the analyzed projects. All of them have more than 5 occurrences per KLOC on average. In particular, two atom candidates occur very frequently, Implicit Predicate (19.89 occurrences per KLOC) and Ternary Operator (10.16 occurrences per KLOC). On the other hand, Arithmetic as Logic and Comma Operator occur less than once for every 50 KLOC.

@@

The results of our survey and interviews suggest that the Ternary Operator does not contribute significantly as a source of misunderstanding (increasing the number of wrong answers in 9\% of the cases, according to our survey). Nonetheless, the Post-Increment Expression and Automatic Semicolon Insertion atoms are listed in the top four sources of misunderstanding  (Table~\ref{tab:difference-correctness}), and also frequently appear in open source systems. As such, fixing the the Post-Increment and Automatic Semicolon Insertion might improve the readabiliy of large amounts of code in JavaScript projects.

>>>>

\begin{table}[htbp]
\caption{Summary of the correctness analysis}
\label{tab:difference-correctness}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
  Atom & Confusing Code & Clean Code & $\Delta$(\%)  \\ \midrule
  Comma Operator                &  28 &  65 & +132   \\ 
  Automatic Semicolon Insertion &  32 &  68 & +112   \\ 
  Post-Increment                &  48 &  64 & +33    \\ 
  Omitted Curly Braces          &  47 &  58 &  +23   \\
  Assignment as Value           &  56 &  68 &  +21   \\ 
  Implicit Predicate            &  58 &  68 &  +17   \\ 
  Logic as Control Flow         &  41 &  48 &  +17   \\ 
  Conditional Operator              &  60 &  66 &  +10   \\ 
  Pre-Increment                 &  50 &  53 &  +6    \\ 
  Arithmetic as Logic           &  64 &  63 &  -2    \\ \bottomrule

@@

{\color{blue}Finally, we also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either \emph{participant education} or \emph{participant experience} impact correctness. The findings suggest that \emph{participant experience} impacts on the results related to correctness (see Figure~\ref{fig:correctness-over-experience}). Even though the presence of atoms of confusion reduces the number of correct answers to all \emph{experience groups}, this effect is not uniform. For instance, novice developers provide a higher number of wrong answers for the confusing version of the code (57.8\%), while developers with more than four years of experience provide more than 70\% of correct answers even when evaluating the confusing version of the code snippets. It is also important to note that, independently of the \emph{experience group}, developers tend to provide more than 84\% of correct answers while predicting the outputs for the clean versions of the code.} {\color{red}We replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistical difference is less significant for those developers with more than ten years of experience.} Differently from \emph{participant experience}, the factor \emph{participant education} does not change substantially the correctness of the answers.

\begin{figure}
  \includegraphics[scale=0.3]{images/correctness-by-experience}
  \caption{Impact of atoms of confusion on the correctness (over the participant experience groups)}
  \label{fig:correctness-over-experience}
\end{figure}

@@

{\color{red}Comparing to previous research, three 
atoms of confusion that Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} confirmed
for \clang and \cpplang do not lead to a statistically significant impact
on correctness in our study: Logic as Control Flow,
Conditional Operator, and Pre-Increment. Our results
support the Gopstein et al. findings for the remaining
atoms. Considering the work of Langhout and Aniche~\cite{Langhout:2021:ACJ},
their work investigates six atom candidates for Java that
we also explore here for JavaScript. Among these atom
candidates, we achieve similar conclusions with their
study for four atom candidates: Post Increment,
Conditional Operator, Arithmetic as Logic, and
Omitted Curly Braces---both studies confirmed only the former
as an atom of confusion. Our findings diverged from
the work of Langhout and Aniche for two atoms: Pre Increment and
Logic as Control Flow.}

\begin{mh}
{\color{red}Comparing the results of different studies,
  the impact of atoms candidates on source code
  (mis)understanding differ according to the programming
  language.}
\end{mh}
%% Regarding the first question we 
%% address in the survey (\emph{Do code snippets that contain atoms of confusion produce a higher error rate than snippets where the atom is removed?}), we found evidence that the atoms of confusion lead programmers to misunderstand JavaScript code. We also realized that just one atom whose correction has a non-significant improvement in the percentage of correct answers---we found an improvement of at least 15\% in the correct answers when removing the confusing code for seven atoms (out of ten atoms we consider in the survey).

@@

\begin{table}[htbp]
\caption{Time in seconds to submit a correct answer}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
Atom & Confusing Code & Clean Code & $\Delta$(\%) \\ \midrule
Comma Operator & 87.67 & 20.84 & -76.23 \\ 
Automatic Semicolon Insertion & 46.08 & 22.04 & -52.17 \\ 
Post-Increment & 28.70 & 25.67 & -10.56 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 \\ 
Conditional Operator & 41.80 & 39.34 & -5.90 \\ 
Pre-Increment & 30.71 & 42.45 & 38.19 \\  
Arithmetic as Logic & 28.82 & 37.20 & 29.06 \\ \bottomrule
\end{tabular}
\label{tab:difference-time-taken}
\end{scriptsize}
}
\end{table}

@@

 \centering
 \begin{tabular}{lccc|cc}
   \toprule
Atom  & Chi-square test & Odds Ratio          & CI & Mann-Whitey U test & Cliff's Delta \\ 
     &         & (misunderstanding)  &                    & (workload)             & \\ \midrule
Comma Operator & 1.1727e-10 & 19.02 & (6.60, 68.22) & 5.8249e-08 & -0.53 \\ 
Automatic Semicolon Insertion & 5.8352e-11 & 39.33 & (9.21, 356.62) & 0.09802 & -0.16 \\ 
Post-Increment & 0.0015279 & 4.83 & (1.73, 15.74) & 0.12006 & 0.15 \\ 
Omitted Curly Braces & 0.050962 & 2.35 & (1.00, 5.77) & 0.92529 & -0.01 \\ 
Assignment as Value & 0.0034775 & 8.39 & (1.81, 79.12) & 0.82681 & 0.02 \\ 
Implicit Predicate & 0.01123 & 6.95 & (1.46, 66.56) & 0.0029039 & -0.29 \\ 
Logic as Control Flow & 0.292 & 1.54 & (0.73, 3.28) & 7.5862e-05 & -0.39 \\ 
Conditional Operator & 0.15896 & 2.73 & (0.74, 12.57) & 0.24073 & -0.12 \\ 
Pre-Increment & 0.70147 & 1.25 & (0.55, 2.85) & 0.0062981 & 0.27 \\ 
Arithmetic as Logic & 1 & 0.84 & (0.22, 3.12) & 0.01723 & 0.23 \\ 
    \bottomrule
 \end{tabular}
 \label{tab:hypothesis-testing}
 \end{table*}

@@

\begin{table}[!htb]
    \centering
    \caption{Summary of participants' preferences for code snippets \emph{with} and
      \emph{without} atom candidates. The participants were only presented the code snippets, without any indication about whether one was confusing or not. 
      Participants were also allowed to choose Neutral when they thought both sides were equally readable.}
    \begin{tabular}{lrrr}\toprule
      & \multicolumn{3}{c}{\textsc{Preference (\%)}} \\
      \cmidrule(lr){2-4}
         Atom           & \multicolumn{1}{c}{Confusing}
                                      &  \multicolumn{1}{c}{Clean}
                                               & \multicolumn{1}{c}{Neutral} \\ \midrule
         Comma Operator                  & 0  & 100    & 0     \\
         Automatic Semicolon Insertion  & 0  & 80     & 0     \\
         Post-Increment                  & 20 & 73.33  & 6.67  \\
         Omitted Curly Braces            & 0  & 100    & 0     \\
         Assignment as Value             & 20 & 60     & 20    \\
         Implicit Predicate              & 20 & 73.33  & 6.67  \\
         Logic as Control Flow           & 20 & 60     & 20    \\
         Conditional Operator                & 60 & 26.67  & 13.3  \\
         Pre-Increment                   & 40 & 46.67  & 13.33 \\ 
         Arithmetic as Logic             & 0  & 93.33  & 6.67  \\ \midrule
         \textsc{overall}                & 18 & 71.33  & 8.64  \\
         \bottomrule
    \end{tabular}
    \label{tab:interview-results1}
\end{table}

\subsubsection*{The Participants' perceptions of the atom candidates}
Supporting the results of the survey, Table~\ref{tab:interview-results1}
 shows that for eight out of the
10 scenarios surveyed, the majority of the respondents prefer the version of the
code without the atom candidate.
In no case the \emph{neutral}
ratio was higher than the option for the clean version.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Conditional Operator atom candidate the participants prefer the Confusing version, instead of the clean one. We show the code snippets for the Conditional Operator in Figure~\ref{code:ternary}. Even for this atom candidate, some participants who preferred the left-hand side version (confusing) still believed that the right-hand side version (clean) was more readable. The following quotes were extracted from the transcripts with
% three interviewees:
two interviewees:

@@

\noindent\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript, caption=\emph{Left-hand side} (using the \emph{Conditional Operator} atom).]
let config = {size: 3, isActive: false};
const_config = config.isActive === true 
             ? config 
             : {size: 10};
console.log(_config.size);
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript, caption=\emph{Right-hand side} (without the atom).]
let config = {size: 3, isActive: false}
let _config;
if(config.isActive === true) {
  _config = config;
}
else{
   _config = {size: 10};
}
console.log(_config.size);
\end{lstlisting}
\end{minipage}
\caption{Example of a pair of code snippets used in the interview. This case explores the use of the \emph{Conditional Operator atom of confusion}}
\label{code:ternary}
\vspace{-0.2cm}
\end{figure*}

@@

We mined \minedprojects open source JavaScript repositories to understand how
often atoms of confusion arise in real software. 
Similarly to previous studies~\cite{DBLP:conf/msr/GopsteinZFC18,DBLP:journals/ese/MedeirosLAAKRG19}, which investigate
the prevalence of atoms of confusion in open source \clang and \cpplang projects, we found that atoms of confusion
frequently arise in JavaScript open source systems. For instance, the six most frequently found atoms
occur in at least 80\% of the projects. Considering the extremes, atom candidates Conditional Operator and Implicit Predicate were found in all repositories we mined,
while Comma Operator occurred in only 15\% of them (as seen in Table~\ref{tab:occurrences-summary}).

@@

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Tue Apr 13 09:34:35 2021
\begin{table}[ht]
\centering
\caption{Summary of atom candidate occurrences on our dataset.}
\setlength\tabcolsep{2pt} % default value: 6pt
\begin{tabular}{lrc}%c}
  \toprule
Atom & Projects & Occurr./KLOC \\%& Frequency \\ 
  \midrule
Implicit Predicate & 100\% & 19.89 \\%&  intensively used \\ 
  Conditional Operator & 100\% & 10.16 \\%&  intensively used \\ 
  Omitted Curly Braces & 91.67\% & 6.61 \\%&  intensively used \\ 
  Post Increment & 90.28\% & 5.62 \\%&  intensively used \\ 
  Pre Increment & 83.33\% & 1.04 \\%& commonly used \\ 
  Assignment as Value & 81.94\% & 1.02 \\%& commonly used \\ 
  Logic as Control Flow & 56.94\% & 0.95 \\%& commonly used \\ 
  Automatic Semicolon Insertion & 33.33\% & 0.13 \\%& commonly used \\ 
  Arithmetic as Logic & 23.61\% & 0.02 \\%& rarely used \\ 
  Comma Operator & 15.28\% & 0.03 \\%& rarely used \\
   \bottomrule
\end{tabular}
\label{tab:occurrences-summary}
\end{table}

Considering all JavaScript projects in our dataset, we found a total of \num{364873} atom candidates, though four atoms are responsible
for 92.97\% of this total: Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces. The first two, based on the results of Section~\ref{sec:survey-resuts}, can be considered atoms of confusion. The remaining atom
candidates comprise \num{25621} occurrences combined, 7.03\% of the total number of occurrences.
The Comma Operator and Arithmetic as Logic atoms are the ones that arise less
frequently (0.001\% in total with 232 and 165 occurrences, respectively).

% Regarding frequency, we proceeded with a classification of \emph{atom occurrence}
% based on thresholds used in a previous
% study~\cite{DBLP:journals/ese/MedeirosLAAKRG19}. 
% Atoms that occur 1000 times are classified as \textit{rarely used} while atoms with more than \num{10000} occurrences are classified as \textit{highly used}; \textit{commonly used} atoms occur in between.
We calculated the frequency of each atom per KLOC.
The four atoms mentioned in the previous paragraph,
 Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces, occur frequently in the analyzed projects. All of them have more than 5 occurrences per KLOC on average. In particular, two atom candidates occur very frequently, Implicit Predicate (19.89 occurrences per KLOC) and Conditional Operator (10.16 occurrences per KLOC). On the other hand, Arithmetic as Logic and Comma Operator occur less than once for every 50 KLOC.

@@

The results of our survey and interviews suggest that the Conditional Operator does not contribute significantly as a source of misunderstanding (increasing the number of wrong answers in 9\% of the cases, according to our survey). Nonetheless, the Post-Increment Expression and Automatic Semicolon Insertion atoms are listed in the top four sources of misunderstanding  (Table~\ref{tab:difference-correctness}), and also frequently appear in open source systems. As such, fixing the the Post-Increment and Automatic Semicolon Insertion might improve the readabiliy of large amounts of code in JavaScript projects.

\todo[inline]{Seria legal contrastar esses achados com o que foi reportado anteriormente}
